% LaTeX resume using res.cls
\documentclass[margin,10pt]{res}
\usepackage{enumitem}
\usepackage{sourcesanspro}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{slantsc}
\usepackage[letterspace=85]{microtype}
\usepackage[style=iso]{datetime2}
\newsectionwidth{0.8in}
\setlist[itemize]{leftmargin=*}
\renewcommand{\familydefault}{\sfdefault}
\name{\begin{minipage}[t]{\textwidth}
Elizabeth Leibel
\vspace{6mm}
\end{minipage}}
\address{\begin{minipage}[t]{\textwidth}
\sc
\lsstyle
\href{https://github.com/EleibelIU}{https://github.com/EleibelIU}
\hfill
liz@leibel.tech
\hfill
630 - 440 - 7163
\hfill
Carmel, Indiana
\\
%\href{https://github.com/dllu}{https://github.com/dllu}
\end{minipage}}
\begin{document}
\begin{resume}
\section{\sc \lsstyle work}
    \href{https://www.gm.com/}{\textbf{General Motors}}, Remote\hfill \textsc{\bfseries\lsstyle 05-2020 -- 08-2020}\\
    \textit{Software Engineering Intern --- Cyber Offense}\hfill \textsc{Python, React, C++}
    \vspace{0.5em}
    \begin{itemize}
        \item Ported DevOps pipeline to Azure for MSU Repel that detects GM IP and PPI leaks in public repositories.
        \item Developed APIs for internal pentesting tools and C2 Frameworks. Created tool monitoring dashboard with MS Teams notification integration to assist in post-pentest forensics. 
        \item Stood up Red-Team focused ELK fork. Developed scrum roadmap for proposed Red Team SIEM.
    \end{itemize}

    \href{https://www.gm.com/}{\textbf{General Motors}}, Austin TX\hfill \textsc{\bfseries\lsstyle 05-2019 -- 08-2019}\\
    \textit{Software Engineering Intern --- Cyber Defense}\hfill \textsc{Go, Python, Tcl, Ruby, C++}
    \vspace{0.5em}
    \begin{itemize}
        \item Drove performance improvements in packet capture for Sguil IDS utilizing Google Stenographer. 
        \item Integrated Sguil with qRadar SIEM and ELK. Automated sensor resource management and created dashboard for sensor topology using scapy and netdata.cloud.
        \item Refactor of Sguil codebase. Stood up DevOps pipeline to for future multithreading features in Sguil. Expanded Unit testing and code coverage.
    \end{itemize}

    \href{}{\textbf{Helvetica Audio}}, Carmel IN\hfill \textsc{\bfseries\lsstyle 08-2019 -- Present}\\
    \textit{Business Owner --- Content Creator}\hfill \textsc{Hadoop, Python, Prometheus, Java Spring}
    \vspace{0.5em}
    \begin{itemize}
        \item Support brands via Big Data:
        \begin{itemize}
            \item Built REST API wrappers for YouTube, TikTok and Twitch. Aggregate Performance, SEO, and keyword/hashtag trains across all major video social media platforms. 
            \item Analyze collected data for best platform algorithm performance. Predict upcoming trends. Automated cross-posting to Patreon and Ko-Fi crowdfunding platforms. 
        \end{itemize}
        \item Offered web design and development services for artists' personal websites. Provided production, mixing, and mastering services to artists. 
    \end{itemize}
\section{\sc \lsstyle Projects}
    \href{https://tethercalc.herokuapp.com/}{\textbf{XIVAnalyis/FFLogs API + Tethercalc}}, \textit{MMO Performance Analytics} \hfill \textsc{\bfseries\lsstyle 08-2011 -- Present}\\
    Prod. API transforms \href{https://www.fflogs.com/}{FFLogs}  output to be parsable by \href{https://xivanalysis.com/}{XIVAnalyis}  and \href{https://tethercalc.herokuapp.com/}{Tethercalc}. \hfill \textsc{Java, React, jQuery}

    \href{https://github.com/spiffytech/DoomBot}{\textbf{NanoWriBot}}, \textit{Discord Bot}\hfill \textsc{\bfseries\lsstyle 11-2020 -- 11-2021}\\
    PM/Sprints for Creative Writing. Supports Toggl, Notion, and Google Docs/Calendar.\hfill \textsc{Java, Kotlin}

    \textbf{Aurora Plugins}, \textit{Collection of VST plugins}\hfill \textsc{\bfseries\lsstyle 06-2017 -- 09-2018}\\
    Open source software emulation of the {\em Yamaha DX7} synth and {\em LA-2A} compressor.\hfill \textsc{C++}

\section{\sc \lsstyle Education}
    \textbf{Indiana University - Bloomington}, B.S. Computer Science \hfill \textsc{\bfseries\lsstyle 2017 -- 2021}\\
    Specialization in Cybersecurity and Risk Management\hfill\\
    %\vspace{5pt}\\
\section{\sc \lsstyle skills}
    \textbf{Languages (Ordered by proficiency):}
    Java, Python, C/C++, Go, SQL, JavaScript/TypeScript, Ruby/Rails  \\
    \textbf{Platforms/Tools:} Azure, AWS, SalesForce, Ansible, Jenkins, Chef, Puppet\\
    \textbf{Certifications:} CompTIA Network+, Security+\\
\end{resume}
\begin{minipage}[t]{\textwidth}
    \flushright
    \small
    \sc \lsstyle
    \hfill updated \today
\end{minipage}
\end{document}
